Rapid-response Bayesian sky localization for electromagnetic follow-up of gravitational-wave candidates

### 2012-05-01 ms.tex
Preliminary abstract

\begin{abstract}
Description of rapid Bayesian sky localization algorithm
\end{abstract}

>>>>

\begin{abstract}
Timely \acl{EM} follow\nobreakdashes-up of \acl{CBC} events detected by \acl{aLIGO} requires rapidly inferring the sky location from the \ac{GW} observations.  Calculation of the posterior distribution of the sky location and intrinsic source parameters given the \ac{GW} strain takes hours with state\nobreakdashes-of\nobreakdashes-the\nobreakdashes-art \ac{MCMC} parameter estimation codes.  By taking as the measurement not the \ac{GW} strain itself but the amplitude and \acl{TOA} of the putative signal at each detector, and by fixing the intrinsic source parameters, we have constructed a non-\ac{MCMC}, fully deterministic Bayesian parameter estimation algorithm that takes just seconds to produce sky maps of posterior probability.%
\marginpar{Wrong emphasis?  I like Larry's idea of having this paper discuss several different tiers of sky localization with increasing accuracy and latency.}
\end{abstract}
